---
title: "PAGnet: an integrated regulatory network in Pseudomonas aeruginosa"
author: 
- name: Hao Huang 
  affiliation: Department of Biomedical Sciences, City University of Hong Kong, Hong Kong
- name: Xiaolong Shao
  affiliation: Key Laboratory of Molecular Microbiology and Technology, Ministry of Education, TEDA Institute of Biological Sciences and Biotechnology, Nankai University, 23 Hongda Street, Tianjin 300457
- name: Yingpeng Xie
  affiliation: Department of Biomedical Sciences, City University of Hong Kong, Hong Kong
- name: Tingting Wang
  affiliation: Department of Biomedical Sciences, City University of Hong Kong, Hong Kong
- name: Yingchao Zhang
  affiliation: Key Laboratory of Molecular Microbiology and Technology, Ministry of Education, TEDA Institute of Biological Sciences and Biotechnology, Nankai University, 23 Hongda Street, Tianjin 300457
- name: Xin Wang
  affiliation: Department of Biomedical Sciences, City University of Hong Kong, Hong Kong
- name: Xin Deng
  affiliation: Department of Biomedical Sciences, City University of Hong Kong, Hong Kong 
date: "`r Sys.Date()`"
package: PAGnet
output: 
        BiocStyle::pdf_document:
          fig_width: 10
          fig_height: 10
        
abstract: PAGnet is an R package to perform Master Regulator Analysis (MRA) for identification of key transcription factors mediating a biological process or pathway in Pseudomonas aeruginosa Genomic netork (PAGnet).

vignette: >
  %\VignetteIndexEntry{HTSanalyzeR2: An R package for gene set enrichment and network analysis of various high-throughput data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE,
                      fig.align   = 'center',
                      fig.width   = 8,
                      fig.height = 4)
```


# Overview
Regulatory networks including virulence-related transcriptional factors (TFs) determine bacterial pathogenicity in response to different environmental cues. Pseudomonas aeruginosa, a Gram-negative opportunistic pathogen of humans, recruits numerous TFs in quorum sensing (QS) system, type III secretion system (T3SS) and Type VI secretion system (T6SS) to mediate the pathogenicity. Although many virulence-related TFs have been illustrated individually, very little is known about their crosstalks and regulatory network. Here, based on chromatin immunoprecipitation coupled with high-throughput sequencing (ChIP-seq) and transcriptome profiling (RNA-seq), we primarily focused on understanding the crosstalks of 19 virulence-related TFs, which led to construction of a virulence regulatory network named PAGnet (Pseudomonas aeruginosa Genomic network) including 48 crosstalk targets.

The PAGnet uncovered the intricate mechanism of virulence regulation and revealed master regulators in QS, T3SS and T6SS pathways. The package **PAGnet** is designed for Master Regulator Analysis (MRA) over a list of regulons from PAGnet. We also provide an online PAGnet platform was established to provide the analysis for these TFs and more virulence factors.

```
## loading packages
library(PAGnet)
```
# Quick Start
### Master Regulator Analysis
The user can choose to use the default PAVIRnet or to upload their own regulatory network in a predefined format.

```{r}
  library(PAGnet)
  data(PAGnet)

  #Use PAGnet as regulatory network
  #Select T3SS related genes as signatures
  #run MRA
  head(PAGnet)
  head(tf)
  head(qs)

```


The function `pagnet.mra` is used to perform MRA in PAGnet or user uploaded network. The MRA computes the overlap between the transcriptional regulatory unities (regulons) and the input signature genes using the hypergeometric distribution.Having completed master regulator analysis, a table will be returned.

```{r}
  mra_results <- pagnet.mra(rnet=PAGnet,tflist=tf,signature = qs, 
                            pValueCutoff = 0.05,pAdjustMethod="BH")
  mra_results
```

To output the MRA results, the user can use `write.csv` to output csv file.

```{r}
  ## write.csv(mra_results,"MRA_results.csv")
```

# Need helps?

If you have any question/issue, please feel free to contact us.

# Session Information
```{r, echo=FALSE}
sessionInfo()
```

# References
